\documentclass[english,10pt,letterpaper]{article}
\usepackage[TextAligned]{currvita}

\usepackage[cm]{fullpage}
\usepackage[absolute,overlay]{textpos}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\usepackage{url}
\usepackage[colorlinks,urlcolor=blue]{hyperref}

\usepackage[pdftex]{color,graphicx}

\usepackage{palatino} % Palatino, Helevetica, Courier

\begin{document}
\centering
\begin{cv}{Juan Antonio Osorio-Robles}

	\begin{table}[h]
		\begin{tabular}{@{} l l p{0.5cm} l r}
			{\bf Personal Information}	&	&	&	{\bf Contact}	&\\
			Date of birth &	January 8, 1990	&	&
			email & \href{mailto:jaosorior@gmail.com}{\tt jaosorior@gmail.com}\\
		\end{tabular}
	\end{table}

	\begin{cvlist}{Introduction}
        \item[\textsc{Summary}]
            I'm a software developer aiming to achieve mastery in Software
            Craftsmanship. Meaning I take time and pride in refining
            methods and practices in order to achieve this. I'm very passionate
            about learning new technologies and building software the best and
            most skillful way that I can.
        %\item[\textsc{Main assets}]
        %    Focus on maintainable, elegant and clean code.\\
        %    I will go as deep as I need to go to fix a problem.\\
        %    Comfortable in big code bases.\\
        %    I will not only focus on the technical side, I will also try to get
        %    a good grasp of the big picture and even the strategy behind it.
	\end{cvlist}


	\begin{cvlist}{Technical Skills}
			\item [\textsc{Languages}]
                Python (main language), C++ (professional experience), C
                (professional experience), bash scripting, Ruby, Java, SQL,
                Javascript
			\item [\textsc{Technologies}]
                OpenStack (Active Technical Contributor), Docker,
                KVM (Basic experience to set my environment for OpenStack),
                Puppet, GStreamer
			\item [\textsc{Development Tools}]
                Git (proficient), Vim (main editor), Gerrit, Subversion,
                Mercurial, GNU Make, CMake
			\item [\textsc{SW Development Methods}]
				Fond of the Continuous Integration for Software.\\
                Test-Driven Development: Given small workshops at work about
                it.\\
                Agile Methodologies (Kanban, Extreme Programming \& Scrum)
			\item [\textsc{Operating Systems}]
                Linux (Archlinux and Fedora as main distros, but have also
                used Ubuntu and Debian to some extent).
	\end{cvlist}

	\begin{cvlist}{Professional Experience}
		\item [September 2015 - present]
            \textbf{Software Developer @ Red Hat} (Finland)\\
            As part of the OpenStack-focused Identity team in Red Hat, my main
            activity has been getting SSL/TLS into Red Hat's main OpenStack
            deployment tool called \textbf{TripleO}. Both for public endpoints
            and internal services. This besides other more ad-hoc activities
            in both the Barbican and TripleO projects.\\

            \href{http://stackalytics.com/?metric=commits&release=all&user_id=jaosorior&company=red\%20hat}
            {\url{http://stackalytics.com/?metric=commits&release=all&user_id=jaosorior&company=red\%20hat}}

		\item [April 2014 - September 2015]
            \textbf{Senior Software Developer @ Ericsson} (Finland)\\
            My main task was to contribute directly to the
            \textbf{OpenStack} project; Here I actively interacted with the
            community, reviewed commits and pushed code to the projects.
            I was also an active contributor to the \textbf{OPNFV}
            initiative; In OPNFV I formed part of the Security Group and
            started the audit-oriented project called \textbf{Inspector}
            there.\\

            \href{http://stackalytics.com/?metric=commits&release=all&user_id=jaosorior&company=ericsson}
            {\url{http://stackalytics.com/?metric=commits&release=all&user_id=jaosorior&company=ericsson}}

            Before this I was part of an integration task force, with the
            aim of creating a sustainable development environment for
            developers to build on. The environment was based on
            \textbf{Docker} in order to ensure the uniformity of
            environments and to create quick and consistent builds.\\

            For a while I was also part of the Cloud Security team where
            I did numerous tasks, such as implement security related
            features; harden and test the security in our cloud solution,
            among other activities.

		\item [June 2012 - April 2014]
            \textbf{Software Developer @ Ericsson} (Finland)\\
            Worked in multimedia-based applications, as a developer in
            Ericsson's Media Gateway. Here, The type and nature of the
            tasks I performed were diverse: I've been taken part in the
            development of high performance multimedia systems; coded
            scripts to aid in version control systems migration (migrated
            from a legacy VCS to \textbf{Git}); took part in in a smaller
            project to develop a visualization of the development process
            within the division; amongst other things.\\

            Aside from that, every once in a while I gave guidance
            regarding open-source processes (licensing and implications).

		\item [July 2011 - December 2011]
            \textbf{Research assistant/Developer @ NIC Mexico} (Monterrey,
            N.L., M\'{e}xico)\\
            Developer lead of a Linux implementation for the \textbf{NAT64}
            mechanism (based on the RFC6146), which had the purpose of
            enabling communication between IPv6 and IPv4 hosts. It was
            implemented as a \textbf{kernel module}, written in \textbf{C},
            working with \textbf{Netfilter}. For user-space control, an
            iptables module was also developed. The implementation is
            open-source:
            \href{http://jool.mx/}{http://jool.mx/} \&\\
            \href{https://github.com/NICMx/NAT64}{https://github.com/NICMx/NAT64}.

		\item [May 2010 - May 2011]
            \textbf{Research assistant @ ITESM} (Monterrey, N.L., M\'{e}xico)\\
            I developed an application (Gadget) for the \textbf{Google Wave}
            platform to collaboratively draw ER diagrams. The project used web
            technologies such as \textbf{HTML5} and the Wave platform's API,
            which is based in \textbf{Java}. Also, I contributed to the
            writing of the research paper, but mostly my role was technical.

		%\item [Summer 2010]
        %    \textbf{Freelance}(Monterrey, N.L., M\'{e}xico)\\
		%	A co-worker and I developed an information system to administer an
        %    apartment complex. It managed the tentants' contracts and payments,
        %    the apartments' availability and the printing of contracts,
        %    receipts and bills.
	\end{cvlist}

    \begin{cvlist}{Community Positions}
		\item [OpenStack]
            I'm a core-developer in the \textbf{Barbican} project (Secret
            Storage As a Service) and \textbf{TripleO} project (OpenStack
            over Openstack - a cloud deployment tool) in the OpenStack
            community.
	\end{cvlist}

    \begin{cvlist}{Other Project(s)}
		\item [January 2012 - May 2012]
            \textbf{Operating Systems Project}(Aalto University, Finland)\\
            With a team consisting of me and two classmates, I successfully
            extended an incomplete operating system, implementing the scheduler,
            system calls, file system, network driver, concurrency manager,
            memory management, a shell, among other things; The target hardware
            was based on the MIPS architecture.
	\end{cvlist}

	\begin{cvlist}{Education}
		\item [January 2012 - December 2012]
			Aalto University, School of Science, Helsinki, Finland\\
			Exchange student. Computer Science Department in the School of
            Science\\
			\href{www.aalto.fi/en}{www.aalto.fi/en}

		\item	[August 2008-- August 2013]
			ITESM, Campus Monterrey. Monterrey N.L., M\'{e}xico\\
			\emph{BCT - B.S. Computer Science and Technology (4.5 years)}\\
			MI - International Modality(
            \href{http://www.mty.itesm.mx/rectoria/dda/dacmi}
            {http://www.mty.itesm.mx/rectoria/dda/dacmi})\\
			Education grade point average: \emph{92/100}
	\end{cvlist}

	%\begin{cvlist}{Awards \& Certifications}
	%	\item [October 2011] Second Place winners of the ITESM's ACM Hackathon.
    %        As a team of 4 members, we developed an application to control a
    %        Linux computer from twitter.(Monterrey, N.L., M\'{e}xico)
	%	\item [August - November 2011] Winners of the ITESM's Business Model
    %        presentation fair and the Business Model Challenge. With a team of
    %        5 we developed the business model for a company called BIOFASE that
    %        sells bioplastic-based products. The project was developed for an
    %        entrepreneurship class and competed with other projects from all
    %        the entrepreneurship classes that semester.
    %        (Monterrey, N.L., M\'{e}xico).
	%	\item [October-December 2011] Successfully finished the Introduction to
    %        Artificial Intelligence with a 90.2/100 grade. \\
	%	    \href{http://ai-class.com}{http://ai-class.com}. (Online course
    %        given in partnership with Stanford Engineering)
	%\end{cvlist}


	\begin{cvlist}{Languages}
		\item [\textsc {Spanish}]
				Native
		\item [\textsc {English}]
				TOEFL IBT: \emph{103/120} - working language
		\item [\textsc {German}]
				Intermediate, 2 years
		\item [\textsc {Finnish}]
				Basic, 1 year
		\end{cvlist}

	\begin{cvlist}{Other Activities}
		\item [2010 - 2012] GULTec - ITESM Linux User Group.\\
			I organized and helped organize technical workshops, which were
            given for free either by me, other members of the group, or by
            professionals. I also was part of the organization of the event
            called ``Interunivesitario de Software Libre''. There, I gave a
            presentation about Open-Source Compliance.
    \end{cvlist}

	\begin{cvlist}{Webpages \& Code Repositories}
        \item [\textsc{Github}]
            \href{http://github.com/JAORMX}{http://github.com/JAORMX}
	\end{cvlist}

\end{cv}

\end{document}
